**The Role of Interoception and Theory of Mind in Deception**

### 2024-06-19 index.Rmd
R2 update
@zen-juen @Tam-Pham back to you for halp

p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing lie", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
p
ggsave("figures/Figure1.png", width=12, height=15)
```

>>>>

p <- (p1 / p2 / p3 / p4 / p5) + plot_layout(guides = "collect") + plot_annotation(title = "Interindividual correlates of the confidence\nthat one tells a convincing response", theme = list(plot.title = element_text(face = "bold", hjust = 0.5)))
p
ggsave("figures/Figure1.png", width=12, height=15)
```
